Insert title of project here

### 2022-04-11 Draft Report/Draft Project.Rmd
Added EJ Screen Data Download source

### Gather Data Sources
```{r load datasources}
# Load your datasets
NRICali <- read.csv('~/Desktop/Duke MPP/Environ Data /872 Final Project/AmanfuJaniRoberton_ENV872_EDA_FinalProject/Potential Data Sources/NRI_Table_CensusTracts_California/NRI_Table_CensusTracts_California.csv', stringsAsFactors = TRUE)
NRINorCar <- read.csv('~/Desktop/Duke MPP/Environ Data /872 Final Project/AmanfuJaniRoberton_ENV872_EDA_FinalProject/Potential Data Sources/NRI_Table_CensusTracts_NorthCarolina/NRI_Table_CensusTracts_NorthCarolina.csv', stringsAsFactors = TRUE)
NRIFlor <- read.csv('~/Desktop/Duke MPP/Environ Data /872 Final Project/AmanfuJaniRoberton_ENV872_EDA_FinalProject/Potential Data Sources/NRI_Table_CensusTracts_Florida/NRI_Table_CensusTracts_Florida.csv', stringsAsFactors = TRUE)
EJScreen21 <- read.csv('~/Desktop/Duke MPP/Environ Data /872 Final Project/AmanfuJaniRoberton_ENV872_EDA_FinalProject/Potential Data Sources/EJSCREEN_2021_StatePctile_Tracts.csv',stringsAsFactors = TRUE)
```

####EJSCREEN Gathered From: 
2020
#### National Risk Index 
Gathered from: <https://hazards.fema.gov/nri/data-resources> North Carolina

### Clean Data Sources

@@

EJScreen21 <- EJScreen21 %>%
  filter(grepl('Florida|California|North Carolina',STATE_NAME))
```

@@

```{r EJScreen Filters}
EJ_filter <- EJScreen21 %>%
  select(ID,STATE_NAME,contains("INCPCT"),contains("HSPCT"),LINGISOPCT,PRE1960PCT,contains("LDPNT"),contains("PM25"))

>>>>

### Gather Data Sources
```{r load datasources}
# Load your datasets
NRICali <- read.csv('~/Desktop/Duke MPP/Environ Data /872 Final Project/AmanfuJaniRoberton_ENV872_EDA_FinalProject/Potential Data Sources/NRI_Table_CensusTracts_California/NRI_Table_CensusTracts_California.csv', stringsAsFactors = TRUE)
NRINorCar <- read.csv('~/Desktop/Duke MPP/Environ Data /872 Final Project/AmanfuJaniRoberton_ENV872_EDA_FinalProject/Potential Data Sources/NRI_Table_CensusTracts_NorthCarolina/NRI_Table_CensusTracts_NorthCarolina.csv', stringsAsFactors = TRUE)
NRIFlor <- read.csv('~/Desktop/Duke MPP/Environ Data /872 Final Project/AmanfuJaniRoberton_ENV872_EDA_FinalProject/Potential Data Sources/NRI_Table_CensusTracts_Florida/NRI_Table_CensusTracts_Florida.csv', stringsAsFactors = TRUE)
EJScreen20 <- read.csv('~/Desktop/Duke MPP/Environ Data /872 Final Project/AmanfuJaniRoberton_ENV872_EDA_FinalProject/Potential Data Sources/EJSCREEN_2020_StatePctile.csv',stringsAsFactors = TRUE)
colnames(EJScreen20)
#colnames(EJScreen21)
#EJScreen21 <- read.csv('~/Desktop/Duke MPP/Environ Data /872 Final Project/AmanfuJaniRoberton_ENV872_EDA_FinalProject/Potential Data Sources/EJSCREEN_2021_StatePctile_Tracts.csv',stringsAsFactors = TRUE)
```

####EJSCREEN Gathered From: 
2020
#### National Risk Index 
Gathered from: <https://hazards.fema.gov/nri/data-resources> North Carolina
And from <https://gaftp.epa.gov/EJSCREEN/2020/> for the EJ Screen Data
### Clean Data Sources

@@

EJScreen20 <- EJScreen20 %>%
  filter(grepl('Florida|California|North Carolina',STATE_NAME))
```

@@

```{r EJScreen Filters}
EJ_filter <- EJScreen20 %>%
  select(ID,STATE_NAME,contains("INCPCT"),contains("HSPCT"),LINGISOPCT,PRE1960PCT,contains("LDPNT"),contains("PM25"))
